Live Functional Programming with Typed Holes

### 2018-10-30 examples-3.tex
Minor clarifications to wording in Example 4

% \begin{subfigure}[t]{\textwidth}
\begin{figure}
\centering
\includegraphics[width=0.71\textwidth,interpolate=false,valign=t]{images/cast-errors.png}
% \includegraphics[width=0.28\textwidth,interpolate=false,valign=t]{images/type-inconsistency.png}
\caption{Example 4: Type Holes and Dynamic Type Errors}
\label{fig:cast-errors}
\vspace{-6px}
\end{figure}
% \end{subfigure}

% So far, we have only discussed incomplete programs where a hole appears within an expression.
In \Hazel, the program can also be incomplete because holes appear in types. 
\citet{popl-paper} confirmed that the literature on \emph{gradual type systems} \cite{Siek06a,DBLP:conf/snapl/SiekVCB15} is directly relevant to the problem of reasoning with type holes, by identifying the type hole with the unknown type. 
% Unsurprisingly, then, it is also relevant to the problem of running 
% programs with type holes. 
Indeed, the purpose of gradual typing is to be able to run programs that are not yet sufficiently annotated with types by inserting \emph{casts} only where necessary. As such, let us consider only a small synthetic example to demonstrate what is unique to our approach.

@@

>>>>

% So far, we have only discussed incomplete programs where a hole appears within an expression.
In \Hazel, the program can also be incomplete because holes appear in types. 
\citet{popl-paper} confirmed that the literature on \emph{gradual type systems} \cite{Siek06a,DBLP:conf/snapl/SiekVCB15} is directly relevant to the problem of reasoning with type holes, by identifying the type hole with the unknown type. 
% Unsurprisingly, then, it is also relevant to the problem of running 
% programs with type holes. 
Gradual type systems can run programs that are not yet sufficiently annotated with types by inserting \emph{casts}  where necessary. We take the same well-studied approach in \Hazel. As such, let us consider only a small synthetic example to demonstrate what is unique to our approach.

@@

% \begin{subfigure}[t]{\textwidth}
\begin{figure}
\centering
\includegraphics[width=0.75\textwidth,interpolate=false,valign=t]{images/cast-errors.png}
% \includegraphics[width=0.28\textwidth,interpolate=false,valign=t]{images/type-inconsistency.png}
\caption{Example 4: Type Holes and Dynamic Type Errors}
\label{fig:cast-errors}
\vspace{-6px}
\end{figure}
% \end{subfigure}
